    \documentclass[margin,line]{resume}
    \usepackage{hyperref}
    \usepackage{amsmath}
    \usepackage{enumitem}
    \usepackage{color}
    \usepackage{verbatim}
    \hypersetup{colorlinks=true,urlcolor=black,linkcolor=black}

\begin{document}
    \begin{center}
    \hspace{-80pt}
    \Large \textbf{Sudharshan Viswanathan}\\
    \hspace{-80pt}
    \large Purdue University
    \end{center}

\begin{resume}
% \maketitle
    %__________________________________________________________________________________________________________________
    % Contact Information    
\vspace{-1mm}
    \section{\mysidestyle Contact \\Information}
   \begin{tabular}{l r}
       \hspace{-10pt} 320 Brown Street, Apartment 517 &\hspace{150pt} \emph{Visa Status:} \hspace{-0.2em} F1 (Student) \\
       \hspace{-10pt} West Lafayette, IN 47906        &\hspace{150pt} \emph{Email:} \href{mailto:viswans@purdue.edu}{viswans@purdue.edu}\\
       \hspace{-10pt} \emph{Phone}: +1 508-654-1337   &\hspace{150pt} \emph{Skype ID:} \hspace{-0.2em} sudharshan.visu \\

    \end{tabular}

\section{\mysidestyle Objective}
Seeking Internship as a Developer during Summer 2016.

\section{\mysidestyle Professional Experience}
        \textbf{Morgan Stanley India} \hfill \textbf{July 2013 - June 2015} \\
        \emph{Quantitative Developer} \hfill Mumbai, India
        \begin{itemize}[leftmargin=*]
\item Date Rolling Library - Developed a \textbf{Stateless Referentially  Transparent Immutable API} while refactoring out the dependency on \textbf{Singleton} pattern within the library in C++. Extended functionality to Java using \textbf{SWIG}
\item Bond Analytics Library - Implementation of feature requests and bug fixes for the proprietary legacy library while matching the industry numbers for the implementation.
\item Implemented \textbf{Line Search minimization} methods separating callbacks from the minimization algorithm. Mentored an internship project in implementing Trust Region Strategies. Implementations to be used in Calibration scenarios across the bank
% \item Integral part of the transition in the development environment of the team. Ensured backward compatibility of the build systems and responsible for setting up and testing of software releases
\end{itemize}

%     \textbf{American Express India} \hfill \textbf{May - July 2012} \\
%     \emph{Internship} \hfill Gurgaon, India
%     \begin{itemize}[leftmargin=*]
% %\hspace{2em}\textit{Risk Modelling of Credit Card Customers based on Initial Transactions} \hfill 
% \item Leveraged the \textbf{Longitudinal Behaviour} of early transactions towards predicting \textbf{Short \& Long Term Risk 
% - Model \textbf{2 times better risk} indication for early defaulters and \textbf{50 bps lower} for good customers than existing methods}
% \item Developed a system that extracts \textbf{risky/credit-worthy behaviour} and flags events across different markets worldwide
% \end{itemize}

%\datedsubsection{Insternship, Ittiam Technologies Pvt Ltd, Bangalore}{May - June 2011}
%\hspace{2em}\textit{Low Density Parity Check(LDPC) models based on the IEEE 802.11n standard}\hfill 
%\item \textbf{Implemented} a model for \textbf{Low Density Parity Check}(LDPC) error correcting codes - based on the IEEE 802.11n standard
%\item Disadvantages of the simple LDPC Encoder- Decoder realized. Proposed a suitable \textbf{Hardware structure} for implementing the LDPC Encoder and Decoder on chip

%\datedsubsection{Agent Technologies Pvt Ltd, Bangalore}{May - June 2010}
%\hspace{2em}\textit{License Plate Extraction for Residential/Retail Usage}\hfill 
%\item \textbf{Image Processing} using Basic Graph Theory. Modular library built in \texttt{C++} - used in extracting License Plate Details. Hit Rate of \textbf{70\%}

\section{\mysidestyle Education}
\textbf{Purdue University} \hfill \textbf{2015-Present} \\
\emph{MS in Computer Science}
    \vspace{2mm} \\
\textbf{Indian Institute of Technology Madras (GPA: 9.06/10) } \hfill \textbf{2008-2013} \\
\emph{B.Tech in Electrical Engineering, M.Tech in VLSI Design and Microelectronics} \\
\emph{Final Year Project} Implemented and Analyzed the Block Based SSTA algorithm on different MT environments:  multi-core and in NVidia GPUs using CUDA while tackling constraints of CUDA architecture. Achieved performance only comparable to serial implementations due to memory bottlenecks.

\section{\mysidestyle Technical \\ Skills} 
Advanced proficiency: C++ \\
Basic proficiency: Java, Scala, Python, PHP

% \section{\mysidestyle Projects}
% \begin{itemize}[leftmargin=*]
% \item Statistical Static Timing Analysis Model (SSTA) based timing algorithms on a GP-GPU - Explored features, methods and drawbacks of different implementations of the algorithm
% \end{itemize}

\section{\mysidestyle Achievements}
    \vspace{-0.0mm}
\begin{itemize}[leftmargin=*]
\item Winner of \href{https://sites.google.com/site/taucontest2013}{\textbf{TAU Contest}}(Variation aware timing contest) 2013 amongst 7 participating international teams. Implemented a multi-threaded Statistical Timing Tool to run on multi-core CPU architecture.
\item Selected for the \textbf{International Olympiad in Informatics Training Camp} in India. Ranked in \textbf{top 25} at the Indian National Olympiad For Informatics.
\item Selected to represent IIT Madras in the \textbf{Indo-German Winter Academy} conducted in December 2011 by IIT Delhi-FAU Erlangen. Presented a Technical Talk on \textbf{Resistive Memory Devices}
%\item \textbf{First} in the Physics Talent Test in January 2008 conducted by The Physics Society, Chennai among \textbf{618} students
%\item Recipient of \textbf{Central Scheme Sector Scholarship} sponsored by the \textbf{MHRD} for excelling in XII CBSE examinations
\end{itemize}


% \datedsubsection{Course Projects}{2010-2012}
% \item Digital VLSI: A Pipelined and Sliding-Window Canny Edge Detector on FPGA (\textit{CAD For VLSI Design).
% Reciprocal and Square Root of Complex Numbers using spline interpolation on FPGA (\textit{DSP Architectures})}

\section{\mysidestyle Positions Of Responsibility}
\textbf{Web And Mobile Operations, Shaastra}
\vspace{1mm}
\begin{itemize}[leftmargin=*]
\item Led a team of 20 coordinators to completely rebuild website for Shaastra, annual technical festival of IIT Madras - in 2 months with \textbf{custom backend} - improved ease of use for Event Coordinators and Participants
\item Laid the foundations for an in-house \textbf{Enterprise Resource Planning}(ERP) system for the organizing team of 300 students
\end{itemize}

\textbf{Election Engineering Team, IIT Madras}
\vspace{1mm}
\begin{itemize}[leftmargin=*]
\item Led the Election Engineering team for the Student Body Elections 2011. Implemented a \textbf{Secure Web Based Voting} for a 5000-strong electorate across 20 polling stations
\end{itemize}

\section{\mysidestyle Extra Curricular Activities}
\begin{itemize}[leftmargin=*]
\item Trained in Vocal Indian Classical Music. Participated in solo competitions held in IIT Madras.
\item Integral part of the Morgan Stanley Cricket team in Corporate Leagues.
%\item Won $3^{rd$ in Online Programming Contest, Exebit 2009, technical festival by CS Dept of IIT Madras.
%Simulation Championship- Won $2^{nd}$ and $3^{rd}$ in Shaastra 2010, Shaastra 2009 respectively}
\end{itemize}
\end{resume}
\end{document}

